% !TEX program = pdflatex
% ATS-friendly single-column resume — standard sections, selectable text, no tables/sidebars
\documentclass[11pt,letterpaper]{article}

\usepackage[margin=0.65in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{setspace}
\usepackage{parskip}

% Mild accent for headers only — body remains plain black for ATS parsers
\definecolor{accent}{HTML}{1F4E79}

\hypersetup{
  colorlinks=true,
  urlcolor=accent,
  pdftitle={Praveen Kasturi - Resume},
  pdfauthor={Praveen Kasturi},
  pdfsubject={Automotive Business Professional}
}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=1.1em, itemsep=0.15em, topsep=0.2em, parsep=0pt}
\setlist[itemize,2]{leftmargin=1.1em, itemsep=0.1em, topsep=0.1em}

\titleformat{\section}
  {\large\bfseries\color{accent}\uppercase}
  {}{0pt}{}[\vspace{-0.4em}\hrule height 0.4pt\vspace{0.55em}]
\titlespacing*{\section}{0pt}{1.1em}{0.4em}

\newcommand{\role}[3]{%
  \textbf{\color{accent}#1}\\[-0.1em]
  \textit{#2}\\[-0.15em]
  {#3}\par\vspace{0.25em}
}

\begin{document}

% ===== HEADER =====
\begin{center}
  {\LARGE\bfseries\color{accent} PRAVEEN KASTURI}\\[0.25em]
  {\large Automotive Business Professional}\\[0.55em]
  \small
  +1\,365\,739\,9161
  $\cdot$
  \href{mailto:kpksuk@yahoo.co.uk}{kpksuk@yahoo.co.uk}
  $\cdot$
  Skype: praveendchamp
  $\cdot$
  \href{https://www.linkedin.com/in/kasturipraveenn/}{linkedin.com/in/kasturipraveenn}
\end{center}

% ===== PROFILE =====
\section{Professional Summary}
Strategic and tactical manager: process-driven, customer-centric, progressive, and passionate professional delivering the highest business standards for automotive distributorship and dealership environments. Proven career of 22+ years in new and pre-owned vehicle sales and Fixed Operations management for multi-site, multi-franchise operations. Hands-on management style with exposure to luxury, premium, and volume automotive brands. Focused on team building through continuous training, customer relationship building, developing loyal clients, and interpersonal skills. Strong in technical, finance, and operational controls. IT-capable and adaptable to any DMS system. 18+ projects successfully delivered during career journey.

% ===== SKILLS =====
\section{Core Competencies}
Sales and network optimization; team building and talent retention; multiple dealer operations; budget and quota allocation; operations management; service and parts management; customer service; technical skills; leadership across front and rear operations.

\section{IT Skills}
Autoline; SAP; Moto Data v10 Titan; IDAMSS; Microsoft Suite. Adaptable to dealership management (DMS) systems.

\section{Automotive Brands}
\textbf{Luxury:} Jaguar Land Rover, BMW, Rolls-Royce, Ford, Audi.\\
\textbf{Volume / Passenger:} Nissan, Honda, Hyundai, Mitsubishi, Chevrolet, Jeep, Dodge, Chrysler, VW, Skoda, Mahindra, Leyland.

% ===== EXPERIENCE =====
\section{Professional Experience}

\role
  {Dealership Fixed Operations Manager}
  {Streetsville Hyundai --- Mississauga, Ontario, Canada}
  {August 2024 -- Present}

\begin{itemize}
  \item Overall dealership performance: vehicle sales volume increased from 800 to 1{,}000 units/year (approx.\ 18\% YOY growth).
  \item Monitored dealership KPIs with positive trends in F\&I and acquisition costs.
  \item Raised inventory from under 200 units to over 300 units with 100\% floor-plan audit control.
  \item Grew Fixed Operations sales by 38\% within one year through SOPs in FOP and dealership operations.
  \item Strengthened financial controls through closer monitoring with Controllers.
  \item Raised customer retention ratio from 62\% to 79\%.
  \item Maintained NPS performance with consistent 10/10 delivery.
  \item Drove PIPO performance within PMA.
  \item Analyzed and set UCD pricing using available system tools.
  \item Drove revenue growth in Fixed Operations and referral of customers to Sales.
\end{itemize}

\vspace{0.45em}
\role
  {Fixed Operations Manager}
  {Nelson GM --- Assiniboia, Saskatchewan, Canada}
  {August 2023 -- July 2024}

\textit{Responsible for Fixed Ops across 4 stores in Saskatchewan province, including Collision, PDR, and Detailing.}
\begin{itemize}
  \item Strategic planner for growth of Fixed Ops business.
  \item Improved dealership performance through flexible operations and floor-plan management.
  \item Completed GM PRO training and warranty trainings.
  \item Established e-commerce platform for spare parts; recorded +32\% growth within the first 100 days.
  \item Cleared sticky inventory via OE Connection portal (approx.\ 21\% liquidation).
\end{itemize}

\vspace{0.45em}
\role
  {Fixed Operations Director}
  {Kewalram Nigeria Limited --- Nigeria}
  {June 2018 -- July 2023}

\begin{itemize}
  \item Award recipient from Foton Daimler International for delivering highest traction in customer retention of loyal clientele.
  \item More than 90\% service client retention, converting to 100\% new-vehicle sales.
  \item Budget planning for 15 branch Fixed Operations; executed successfully.
  \item Established VAS at the dealership including Bosch (FIP Service) and wholesale of parts (sticky lines).
  \item Set up stores in Lagos, Abuja, and Port Harcourt.
\end{itemize}

\vspace{0.45em}
\role
  {GM Aftersales (JLR) / Body Shops --- Aluminum Body Repair Centre (Rolls-Royce, JLR, BMW, Ford)}
  {Coscharis Motors Ltd --- Nigeria}
  {November 2014 -- March 2018}

\begin{itemize}
  \item Gold Award recipient --- 2016, 2017 Best Service Manager.
  \item Best Dealership for Jaguar and Land Rover 2016 and 2017.
  \item Raised Dealer Service Experience from 74\% to 92\%.
  \item Revenue-line growth with absorption ratio of 75\%.
  \item Started aluminum body repair center operations; standardized tooling and equipment for Rolls-Royce, JLR, BMW, and Ford.
  \item Increased NPS in conjunction with mystery-shopper experience.
  \item Customer retention program for JLR brand; increased sales by 35\%.
  \item Rolled out regional pilot projects: CLP, 5-year warranty and service, DSE, TAT reports.
  \item Consistently achieved P\&A sales quotas over +20\%.
  \item Built Service Advisors and technical teams through continuous E-learning monitoring.
  \item Regional Best Technician award for team members twice; nominated for global competition.
\end{itemize}

\vspace{0.45em}
\role
  {National Aftersales Manager / National Service Manager}
  {CFAO Automotive --- Nigeria}
  {February 2007 -- November 2014}

\begin{itemize}
  \item Supported Nissan and Renault sales and dealership network development through SOP implementation.
  \item Set up dealership service, collision center, and express service centers across Lagos (VI and Amuwo Odofin).
  \item Recruited Service, Parts, and Collision Center personnel.
  \item Designed shop and body-shop layouts for effective flow control and efficiency.
  \item Grew Nissan market share from 1.25\% to 7.5\% within 3 years of relaunch.
  \item Established Accident Repair Center by consolidating NSC operations.
\end{itemize}

\vspace{0.45em}
\role
  {Sr.\ Branch Manager / Branch Manager --- North Region}
  {Stallion Group --- Nigeria}
  {June 2001 -- December 2006}

\begin{itemize}
  \item \textbf{Branch Manager --- Honda Cars 3S Dealership} (2001--2004, Northern Region --- Kano)
    \begin{itemize}
      \item SSI / CSI scoring +92\%.
      \item Increased vehicle sales by 220\%.
    \end{itemize}
  \item \textbf{Branch Manager --- CBD Abuja} (2004 -- February 2005)
    \begin{itemize}
      \item Multi-franchise dealership: Honda, Hyundai, VW Group.
      \item Average unit sales of 75/month.
      \item Workshop layout design and project commencement.
      \item Market penetration for Hyundai; institutional and government sales relationship building.
    \end{itemize}
  \item \textbf{Sr.\ Branch Manager --- Port Harcourt} (2005--2006)
    \begin{itemize}
      \item Built relationships with Oil \& Gas companies (Shell, Agip, Total) and oil support services.
      \item Increased vehicle sales by 33\% in the region.
      \item New vehicle sales through cooperatives; CSI 94\% in aftersales.
      \item Built strong group foundation; regional market share of sales more than 72\% across brands.
    \end{itemize}
\end{itemize}

\vspace{0.45em}
\subsection*{\color{accent}Early Career --- India (Automotive Dealership)}
\begin{itemize}
  \item 1998--2001: Workshop Manager and Assistant Service Manager --- Honda, GM.
  \item 1998--1999: Workshop Manager --- TATA Passenger Cars.
  \item 1996--1998: Management Trainee / Training In-Charge --- Suzuki Dealer.
\end{itemize}

% ===== VOLUNTARY =====
\section{Voluntary Services}
\begin{itemize}
  \item Community leadership with TAN in Nigeria --- progressed from General Secretary to President; raised more than \$95{,}000 for charitable events.
  \item Rescued 225 people of Indian origin to safely reach Hyderabad, India during COVID-19 (June 2020).
  \item Conducted charity campaigns supporting underprivileged communities in Lagos, Nigeria.
  \item Organized community events for 415 participants (beach picnic); managed a team of more than 20 leaders.
  \item Raised funds in money and kind to support people affected by COVID-19 and isolation centers.
\end{itemize}

% ===== EDUCATION =====
\section{Education}
\textbf{Automobile Engineering} --- Distinction.

% ===== INTERESTS =====
\section{Interests}
Community service and charitable organizations; travel and long drives; table tennis; music; swimming.

\end{document}
